### 2020-08-10 benchmarking/benchmarkingVM/ESS_round1_real.tex
results update

% Created by tikzDevice version 0.12.3 on 2020-08-07 14:28:24
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}
\usepackage[active,tightpage,psfixbb]{preview}
\PreviewEnvironment{pgfpicture}
\setlength\PreviewBorder{0pt}
\usepackage{amssymb}\begin{document}

@@

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54,548.96) {\bfseries Comparison of cons (\textit{real}) and nocons (\textit{real})};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54,301.03) {ESS/chain [nocons (\textit{real})]};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at ( 17.93,433.62) {ESS/chain [cons (\textit{real})]};
\end{scope}
\begin{scope}
\path[clip] ( 49.80,338.88) rectangle (239.28,528.36);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{gray}{0.91}

\path[draw=drawColor,line width= 0.1pt,line join=round,line cap=round,fill=fillColor] (  0.00,365.38) --
	(212.78,578.16) --
	(281.53,578.16) --
	(281.53,494.30) --
	(  0.00,212.78) --
	cycle;
\definecolor{fillColor}{RGB}{190,190,190}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round,fill=fillColor] (  0.00,339.95) --
	(238.21,578.16) --
	(281.53,578.16) --
	(281.53,519.74) --
	(  0.00,238.21) --
	cycle;
\definecolor{fillColor}{RGB}{169,169,169}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (  0.00,314.51) --
	(263.65,578.16) --
	(281.53,578.16) --
	(281.53,545.17) --
	(  0.00,263.65) --
	cycle;

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (133.64,342.31) {$\frac{1}{64} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,426.62) {$64\times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (108.20,342.31) {$\frac{1}{16} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,401.18) {$16\times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 81.11,342.31) {$\frac{1}{4} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 51.92,375.75) {$4\times$};

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 49.80,338.88) -- (239.28,528.36);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (153.14,457.67) --
	(163.00,457.67);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (158.72,454.14) --
	(158.72,460.63);
\definecolor{drawColor}{RGB}{255,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (158.72,454.44) {$p$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (203.97,498.27) --
	(218.78,498.27);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (212.83,495.92) --
	(212.83,500.36);
\definecolor{drawColor}{RGB}{255,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (212.83,494.24) {$L$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (178.45,498.59) --
	(180.15,498.59);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (179.32,497.51) --
	(179.32,499.62);
\definecolor{drawColor}{RGB}{255,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (179.32,494.56) {$r$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (146.49,453.46) --
	(152.86,453.46);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (149.95,449.76) --
	(149.95,456.55);
\definecolor{drawColor}{RGB}{255,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (149.95,449.43) {$h$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (156.64,437.17) --
	(165.01,437.17);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (161.30,434.91) --
	(161.30,439.18);
\definecolor{drawColor}{RGB}{255,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (161.30,434.26) {$\sigma$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.32,508.76) --
	(221.15,508.76);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.74,507.98) --
	(220.74,509.51);
\definecolor{drawColor}{RGB}{255,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (220.74,505.85) {$\mu$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (192.30,494.32) --
	(194.81,494.32);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (193.60,491.54) --
	(193.60,496.74);
\definecolor{drawColor}{RGB}{0,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (193.60,491.10) {$p$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (205.85,498.07) --
	(214.19,498.07);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (210.49,494.17) --
	(210.49,501.29);
\definecolor{drawColor}{RGB}{0,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (210.49,494.04) {$L$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (209.48,503.25) --
	(210.75,503.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (210.13,501.60) --
	(210.13,504.76);
\definecolor{drawColor}{RGB}{0,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (210.13,499.21) {$r$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (193.18,482.71) --
	(198.08,482.71);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (195.79,479.66) --
	(195.79,485.33);
\definecolor{drawColor}{RGB}{0,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (195.79,478.68) {$h$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.48,485.22) --
	(198.60,485.22);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (197.57,481.89) --
	(197.57,488.04);
\definecolor{drawColor}{RGB}{0,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (197.57,482.32) {$\sigma$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (222.10,512.25) --
	(223.18,512.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (222.65,510.74) --
	(222.65,513.65);
\definecolor{drawColor}{RGB}{0,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (222.65,509.35) {$\mu$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (197.17,469.31) --
	(197.17,474.08);
\definecolor{drawColor}{RGB}{0,255,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (197.17,468.62) {$p$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (214.45,504.24) --
	(220.93,504.24);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (217.97,503.56) --
	(217.97,504.90);
\definecolor{drawColor}{RGB}{0,255,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (217.97,500.21) {$L$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (208.42,505.36) --
	(222.61,505.36);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (216.85,505.09) --
	(216.85,505.62);
\definecolor{drawColor}{RGB}{0,255,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (216.85,501.33) {$r$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (169.48,442.96) --
	(169.48,453.47);
\definecolor{drawColor}{RGB}{0,255,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (169.48,444.93) {$h$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.56,462.82) --
	(196.56,467.56);
\definecolor{drawColor}{RGB}{0,255,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (196.56,462.44) {$\sigma$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (222.70,512.26) --
	(223.15,512.26);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (222.93,512.04) --
	(222.93,512.48);
\definecolor{drawColor}{RGB}{0,255,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (222.93,509.36) {$\mu$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (192.68,478.88) --
	(192.68,485.07);
\definecolor{drawColor}{RGB}{255,255,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (192.68,479.01) {$p$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (148.72,496.18) --
	(218.04,496.18);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (205.74,494.03) --
	(205.74,498.10);
\definecolor{drawColor}{RGB}{255,255,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (205.74,492.14) {$L$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (217.70,503.25) --
	(229.53,503.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (224.55,502.95) --
	(224.55,503.55);
\definecolor{drawColor}{RGB}{255,255,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (224.55,499.22) {$r$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (173.85,475.04) --
	(211.32,475.04);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (200.84,472.97) --
	(200.84,476.90);
\definecolor{drawColor}{RGB}{255,255,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (200.84,471.00) {$h$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (206.62,480.49) --
	(206.62,483.96);
\definecolor{drawColor}{RGB}{255,255,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (206.62,479.40) {$\sigma$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (222.33,511.89) --
	(223.37,511.89);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (222.86,511.27) --
	(222.86,512.49);
\definecolor{drawColor}{RGB}{255,255,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (222.86,508.99) {$\mu$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (221.91,482.52) --
	(221.91,491.18);
\definecolor{drawColor}{RGB}{255,165,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (221.91,484.13) {$p$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (202.65,482.61) --
	(202.65,488.22);
\definecolor{drawColor}{RGB}{255,165,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (202.65,481.59) {$L$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (199.21,500.97) --
	(230.61,500.97);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.94,500.31) --
	(220.94,501.61);
\definecolor{drawColor}{RGB}{255,165,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (220.94,496.94) {$r$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (169.32,486.64) --
	(193.67,486.64);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (185.26,482.99) --
	(185.26,489.69);
\definecolor{drawColor}{RGB}{255,165,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (185.26,482.61) {$h$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (207.68,479.70) --
	(207.68,488.91);
\definecolor{drawColor}{RGB}{255,165,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (207.68,481.98) {$\sigma$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (119.95,439.54) --
	(137.90,439.54);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (131.04,432.27) --
	(131.04,444.73);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (131.04,436.31) {$p$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (204.56,498.07) --
	(210.93,498.07);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (208.02,496.36) --
	(208.02,499.62);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (208.02,494.03) {$L$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (125.81,497.45) --
	(135.01,497.45);

>>>>

% Created by tikzDevice version 0.12.3 on 2020-08-10 16:04:15
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}
\usepackage[active,tightpage,psfixbb]{preview}
\PreviewEnvironment{pgfpicture}
\setlength\PreviewBorder{0pt}
\usepackage{amssymb}\begin{document}

@@

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54,548.96) {\bfseries cons (\textit{real}) vs. nocons (\textit{real})};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54,301.03) {ESS/hr [nocons (\textit{real})]};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at ( 17.93,433.62) {ESS/hr [cons (\textit{real})]};
\end{scope}
\begin{scope}
\path[clip] ( 49.80,338.88) rectangle (239.28,528.36);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (  0.00,374.64) --
	(203.52,578.16);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (286.65,578.16) --
	(286.65,490.17) --
	(  0.00,203.52);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (  0.00,346.12) --
	(232.04,578.16);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (286.65,578.16) --
	(286.65,518.69) --
	(  0.00,232.04);

\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (  0.00,317.60) --
	(260.56,578.16);

\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (286.65,578.16) --
	(286.65,547.21) --
	(  0.00,260.56);

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (142.89,342.31) {$\frac{1}{64} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,435.87) {$64\times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (114.37,342.31) {$\frac{1}{16} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,407.35) {$16\times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 84.20,342.31) {$\frac{1}{4} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 51.92,378.83) {$4\times$};

\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] ( 49.80,338.88) -- (239.28,528.36);
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 86.08,409.37) --
	(106.21,409.37);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 98.51,401.22) --
	( 98.51,415.19);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 98.51,406.14) {$p$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (180.95,474.99) --
	(188.09,474.99);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (184.83,473.08) --
	(184.83,476.74);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (184.83,470.96) {$L$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 92.65,474.30) --
	(102.96,474.30);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 98.44,471.52) --
	( 98.44,476.75);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 98.44,470.27) {$r$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 85.75,424.33) --
	( 97.88,424.33);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 92.70,416.17) --
	( 92.70,430.15);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 92.70,420.29) {$h$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 85.46,386.96) --
	(113.76,386.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (104.13,378.15) --
	(104.13,393.10);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (104.13,384.05) {$\sigma$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (193.32,483.57) --
	(194.53,483.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (193.94,482.97) --
	(193.94,484.15);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (193.94,480.66) {$\kappa$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (167.20,470.80) --
	(170.02,470.80);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (168.66,467.68) --
	(168.66,473.50);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (168.66,467.57) {$p$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.39,475.00) --
	(191.75,475.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (187.60,470.62) --
	(187.60,478.61);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (187.60,470.96) {$L$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (186.47,480.80) --
	(187.89,480.80);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (187.19,478.95) --
	(187.19,482.50);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (187.19,476.77) {$r$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (168.19,457.78) --
	(173.69,457.78);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (171.12,454.35) --
	(171.12,460.71);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (171.12,453.74) {$h$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (171.89,460.59) --
	(174.27,460.59);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (173.11,456.85) --
	(173.11,463.75);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (173.11,457.69) {$\sigma$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.58,485.03) --
	(197.77,485.03);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.24,483.39) --
	(196.24,486.55);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (196.24,482.13) {$\kappa$};
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (172.67,442.74) --
	(172.67,448.10);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (172.67,442.37) {$p$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (192.04,481.91) --
	(199.30,481.91);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (195.99,481.15) --
	(195.99,482.65);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (195.99,477.88) {$L$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (185.28,483.17) --
	(201.19,483.17);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.73,482.87) --
	(194.73,483.47);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.73,479.14) {$r$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (141.61,413.21) --
	(141.61,424.99);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (141.61,415.90) {$h$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (171.98,435.47) --
	(171.98,440.78);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (171.98,435.39) {$\sigma$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (197.52,487.53) --
	(197.96,487.53);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (197.74,487.09) --
	(197.74,487.96);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (197.74,484.63) {$\kappa$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (135.67,450.29) --
	(147.06,450.29);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (142.14,448.74) --
	(142.14,451.73);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (142.14,447.06) {$p$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (190.48,480.63) --
	(196.33,480.63);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (193.61,479.97) --
	(193.61,481.28);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (193.61,476.60) {$L$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (179.06,479.97) --
	(184.03,479.97);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (181.70,479.64) --
	(181.70,480.30);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (181.70,475.94) {$r$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (131.78,442.10) --
	(143.02,442.10);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (138.16,440.36) --
	(138.16,443.70);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (138.16,438.06) {$h$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (132.72,440.69) --
	(144.81,440.69);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (139.64,439.60) --
	(139.64,441.72);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (139.64,437.78) {$\sigma$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (197.55,488.06) --
	(198.21,488.06);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (197.88,487.69) --
	(197.88,488.42);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (197.88,485.15) {$\kappa$};
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (123.29,429.70) --
	(134.35,429.70);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (129.55,425.74) --
	(129.55,433.02);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (129.55,426.47) {$p$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (180.28,475.22) --
	(196.89,475.22);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (190.22,472.58) --
	(190.22,477.56);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (190.22,471.19) {$L$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (151.67,475.58) --
	(153.58,475.58);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (152.65,474.36) --
	(152.65,476.74);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (152.65,471.55) {$r$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (115.83,424.98) --
	(122.98,424.98);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (119.72,420.83) --
	(119.72,428.44);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (119.72,420.95) {$h$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (127.22,406.71) --
	(136.61,406.71);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (132.44,404.17) --
	(132.44,408.97);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (132.44,403.80) {$\sigma$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (195.61,485.43) --
	(196.23,485.43);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (195.92,484.44) --
	(195.92,486.37);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (195.92,482.52) {$\kappa$};
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (167.63,453.48) --
	(167.63,460.42);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (167.63,454.02) {$p$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (118.33,472.88) --
	(196.07,472.88);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.27,470.47) --
	(182.27,475.03);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (182.27,468.84) {$L$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (195.68,480.81) --
	(208.94,480.81);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (203.36,480.47) --
	(203.36,481.14);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (203.36,476.77) {$r$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (146.51,449.17) --
	(188.52,449.17);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (176.77,446.85) --
	(176.77,451.26);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (176.77,445.14) {$h$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (183.26,455.28) --
	(183.26,459.17);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (183.26,454.41) {$\sigma$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.59,486.76) --
	(197.77,486.76);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (197.19,486.27) --
	(197.19,487.23);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (197.19,483.85) {$\kappa$};
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (105.42,469.49) --
	(156.55,469.49);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (143.93,468.42) --
	(143.93,470.50);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (143.93,466.26) {$p$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (148.45,480.12) --
	(196.70,480.12);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (184.33,479.27) --
	(184.33,480.94);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (184.33,476.09) {$L$};
